Simulation of Nano Particles in a Laser Trap

### 2017-02-02 doc/draft2.tex
added test for 1 gas particle

>>>>

With these four temperatures introduced, some questions arise about the relationship between these temperatures. For this theses, I want to focus on
the question: how does the laser intensity influence the motion of the nano particle in the laser trap and its center of mass velocity?\\
In the next section I will introduce the methods that will be used to simulate the system, followed by the results of the simulations and the
conclusion of this thesis.
